### 2017-11-02 paper/sections/1_introduction.tex
paper: new intro, title, abstract
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% What is Mantle
To explore the effects of different cache management strategies, we link the
Mantle policy engine into ParSplice~\cite{perez:jctc20150parsplice}.
Developers write policies for ``when" they want data moved, ``where" they want
data moved, and ``how much" of the data to move and the framework executes
these policies whenever a decision needs to be made.  This abstraction helps
developers unfamiliar with the domain quickly reason about, develop, and deploy
new policies that control temporal and spatial locality.  It has already proven
to be a critical control plane for improving file system metadata load
balancing~\cite{sevilla:sc15-mantle} and in this work we show its usefulness in
cache management for the changing key-value workloads generated by ParSplice.

% What are we going to show
We show how Mantle:
\begin{itemize}

@@

This last contribution is explored in Section~\S\ref{sec:mantle-brains}, where
we try a range of policies from different disciplines; but more importantly, in
Section~\S\ref{sec:relation-to-file-systems}, we conclude that the collection
of policies we designed for ParSplice's cache management are very similar to
the policies implemented in the Ceph file system metadata load balancer. This
lays the foundation for future work, where we will focus on formalizing a
collection of general data management policies that can be used across domains
and services. The value of such a collection eases the burden of policy
development and paves the way for solutions that remove the administrator from
the development cycle, such as (1) adaptable policies that automatically switch
to new strategies when the current strategy behaves poorly ({e.g.}, thrashing,
making no progress, etc.), and (2) policy generation, where new policies are
constructed automatically by examining the collection of existing policies.
Such work is made possible with Mantle's ability to dynamically change
policies.

>>>>

% What is Mantle
To explore the effects of different cache management strategies, we link the
Mantle policy engine into ParSplice.  Mantle~\cite{sevilla:sc15-mantle} has
already proven to be a critical control plane for improving file system
metadata load balancing  and in this work we show its usefulness in cache
management for the changing key-value workloads generated by ParSplice.
Developers write policies for ``when" they want data moved, ``where" they want
data moved, and ``how much" of the data to move and the framework executes
these policies whenever a decision needs to be made.  This abstraction helps
developers unfamiliar with the domain quickly reason about, develop, and deploy
new policies that control temporal and spatial locality. We show that Mantle:

\begin{itemize}

@@

This last contribution is explored in Section~\S\ref{sec:mantle-brains}, where
we try a range of policies from different disciplines; but more importantly, in
Section~\S\ref{sec:relation-to-file-systems}, we conclude that the collection
of policies we designed for ParSplice's cache management are very similar to
the policies in the Ceph file system that are used to load balance metadata.
This lays the foundation for future work, where we will focus on formalizing a
collection of general data management policies that can be used across domains
and services. The value of such a collection eases the burden of policy
development and paves the way for solutions that remove the administrator from
the development cycle, such as (1) adaptable policies that automatically switch
to new strategies when the current strategy behaves poorly ({e.g.}, thrashing,
making no progress, etc.), and (2) policy generation, where new policies are
constructed automatically by examining the collection of existing policies.
Such work is made possible with Mantle's ability to dynamically change
policies.
